Copulas and their potential for ecology: Appendices for main text

### 2019-12-20 SupportingInformation.Rmd
adding short notation
test case: endline editing, committing from linux for change made in windows

---
title: "Copulas and their potential for ecology: Appendices"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance D. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

knitr::kable(NA, "latex", booktabs = T, linesep = "", escape=F,
      caption = "Summary of principal notation. Many notations are defined and used only within a small part of the paper. This table summarizes notation that is used across larger portions of the paper. Section headers refer to the section in which the notation was originally defined. cdf = cumulative distribution function. \\label{tab_summary_notation}")
```

>>>>

---
title: "Copulas and their potential for ecology: Appendices for main text"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance D. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

knitr::kable(NA, "latex", booktabs = T, linesep = "", escape=F,
             caption.short = "Summary of principal notation",
      caption = "Summary of principal notation. Many notations are defined and used only within a small part of the paper. This table summarizes notation that is used across larger portions of the paper. Section headers refer to the section in which the notation was originally defined. cdf = cumulative distribution function. \\label{tab_summary_notation}")
```
